Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-26 paper/main.Rmd
structure change with runs pairwise and mmpd raw included

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE,
        tinytex.verbose = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)
library(kableExtra)
library(distributional)
library(ggplot2)
library(sugrrants)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                                read_chunk('main.R')
read_chunk("null_distribution.R")
read_chunk("mean_null.R")
source("R/sim_panel.R")
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```

@@

```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
elec <- read_rds("data/elec.rds") %>% 
  filter(date >= ymd("20180101"), date < ymd("20180701"))
rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")

@@

@@

### Distribution
<!-- ### Need for normalisation -->

@@

```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown. The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained. "}
mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds") 
mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds") 
mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds")

data_all = bind_rows(mmpd_raw, mmpd_xmore)

data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels")

g1 <- data_all %>% 
  filter(!(nx %in% c(3, 4))) %>% 
  ggplot() +
  ggridges::geom_density_ridges(aes(x = raw_mmpd, 
                                    y = as.factor(nfacet))) +
  facet_wrap(~nx, nrow = 2)
g1
```

```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown. The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases. "}
g2 <- data_all %>% 
  filter(nfacet<=14, nfacet!=3) %>% 
  ggplot() +
  geom_boxplot(aes(y = raw_mmpd, 
                                    x = as.factor(nx))) +
  facet_wrap(~nfacet) + coord_flip()

#  hist_plot = data_all %>% 
#       ggplot() +
#       geom_density(aes(x = raw_mmpd), fill = "blue") +
#       facet_grid(nx~nfacet)
# hist_plot
g2
```

@@

```{r}
knitr::include_graphics("Figs/simulation.png")
```

@@

cricket_all <- read_csv("data-raw/deliveries_all.csv")
matches_all <- read_csv("data-raw/matches_all.csv")

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE,
        tinytex.verbose = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)
library(kableExtra)
library(distributional)
library(ggplot2)
library(sugrrants)
library(here)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                                read_chunk('main.R')
here::here()
read_chunk(here::here("paper/R/", "null_distribution.R"))
read_chunk(here::here("paper/R/", "mean_null.R"))
source(here::here("paper/R/sim_panel.R"))
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```

@@

```{r calendar-elec, fig.height = 10.5, fig.cap="Calendar display."}
elec <- read_rds(here("paper/data/elec.rds")) %>% 
  filter(date >= ymd("20180101"), date < ymd("20180701"))
rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")

@@

sim_varf_dist1 = function(nx, nfacet){
  rep(dist_normal(seq(mean,mean*nfacet, by = mean), sd), each = nx)}

@@

# Behavior of raw distance measure

## Distribution
<!-- ### Need for normalisation -->

@@

```{r hist-nx-nfacet}
knitr::include_graphics(here::here("simulations/result_report/hist_nxbyfacet.png"))
```

```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown. The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained."}
here::here()
knitr::include_graphics(here::here("simulations/result_report","nx_by_facet_raw.png"))
```

<!-- # ```{r dist-across-facets, fig.cap = "Distribution of $MMPD_{raw}$ for different facet levels are shown. The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained. "} -->
<!-- # mmpd_raw = read_rds("../hakear-drake/data/data_all23457914n.rds")  -->
<!-- # mmpd_xmore = read_rds("../hakear-drake/data/data_all213045x.rds")  -->
<!-- # mmpd_fmore = read_rds("../hakear-drake/data/data_all_213045f_allx.rds") -->
<!-- #  -->
<!-- # data_all = bind_rows(mmpd_raw, mmpd_xmore) -->
<!-- #  -->
<!-- # data_long = data_all %>% pivot_longer(c(1:2), names_to = "category", values_to = "levels") -->
<!-- #  -->
<!-- # g1 <- data_all %>%  -->
<!-- #   filter(!(nx %in% c(3, 4))) %>%  -->
<!-- #   ggplot() + -->
<!-- #   ggridges::geom_density_ridges(aes(x = raw_mmpd,  -->
<!-- #                                     y = as.factor(nfacet))) + -->
<!-- #   facet_wrap(~nx, nrow = 2) -->
<!-- # g1 -->
<!-- # ``` -->

```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown. The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases. "}
knitr::include_graphics(here::here("simulations/result_report/","nfacet_by_nx_raw.png"))
```

<!-- # ```{r dist-across-x, fig.cap = "Distribution of $MMPD_{raw}$ for different x levels are shown. The scale of the distribution becomes less and less implying that as the number of x levels increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained as the spread of the distribution decreases. "} -->
<!-- # g2 <- data_all %>%  -->
<!-- #   filter(nfacet<=14, nfacet!=3) %>%  -->
<!-- #   ggplot() + -->
<!-- #   geom_boxplot(aes(y = raw_mmpd,  -->
<!-- #                                     x = as.factor(nx))) + -->
<!-- #   facet_wrap(~nfacet) + coord_flip() -->
<!-- #  -->
<!-- # #  hist_plot = data_all %>%  -->
<!-- # #       ggplot() + -->
<!-- # #       geom_density(aes(x = raw_mmpd), fill = "blue") + -->
<!-- # #       facet_grid(nx~nfacet) -->
<!-- # # hist_plot -->
<!-- # g2 -->
<!-- # ``` -->

@@

```{r}
knitr::include_graphics(here::here("paper/Figs/simulation.png"))
```

@@

cricket_all <- read_csv("paper/data-raw/deliveries_all.csv")
matches_all <- read_csv("paper/data-raw/matches_all.csv")
